Pyro -Velocity: Probabilistic RNA Velocity inference from single-cell data

### 2025-03-23 reproducibility/manuscript/v2.tex
chore(manuscript): update v2 diff file

\raggedbottom
\usepackage{nameref}
\usepackage{placeins}
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\usepackage[labelfont=bf]{caption}
% \usepackage{showframe}
% \usepackage{layout}
\allowdisplaybreaks
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{suppfig}{h}{loextfig}}{\newfloat{suppfig}{h}{loextfig}[chapter]}
\floatname{suppfig}{Extended Data Fig.}
\newcommand*\listofsuppfigs{\listof{suppfig}{List of Extended Data Figures}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\includegraphics{figures/v2/Figure1.pdf}

@@

\includegraphics{figures/v2/Figure2.png}

@@

\includegraphics{figures/v2/Figure3.png}

@@

\includegraphics{figures/v2/Supplementary-Figure1.pdf}

@@

\includegraphics{figures/v2/Supplementary-Figure2.png}

@@

\includegraphics{figures/v2/Supplementary-Figure3.png}

@@

\includegraphics{figures/v2/Supplementary-Figure4.png}

@@

\includegraphics{figures/v2/Supplementary-Figure5.png}

>>>>

\raggedbottom
\usepackage{nameref}
\usepackage{placeins}
\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\usepackage[labelfont=bf]{caption}
% \usepackage{showframe}
% \usepackage{layout}
\allowdisplaybreaks

\let\oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[2][]{\oldincludegraphics[#1,keepaspectratio]{#2}}
\makeatletter
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{plain}
\@ifundefined{c@chapter}{\newfloat{suppfig}{h}{loextfig}}{\newfloat{suppfig}{h}{loextfig}[chapter]}
\floatname{suppfig}{Extended Data Fig.}
\newcommand*\listofsuppfigs{\listof{suppfig}{List of Extended Data Figures}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Figure1.pdf}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Figure2.png}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Figure3.png}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Supplementary-Figure1.pdf}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Supplementary-Figure2.png}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Supplementary-Figure3.png}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Supplementary-Figure4.png}

@@

\includegraphics[width=0.98\textwidth,height=\textheight]{figures/v2/Supplementary-Figure5.png}
